% !TeX root = ../main.tex
% Add the above to each chapter to make compiling the PDF easier in some editors.

\chapter{Problem}\label{chapter:problem}

\section{Setting}

In the following we are going to model a network auction setting, which we then use to define our goals and the steps required in order to reach these goals. The setting for our problem is a procurement auction in which the auctioneer is able to purchase connections from different sellers in order to connect a set of nodes. The true valuations of the connections are known only to their respective sellers and they may choose to prize them any way they want. We know about these sellers that they are single minded and therefore only care about increasing their personal payoff. In order to connect the required nodes the auctioneer may choose to include other nodes, since they may help connect the required nodes and therefore reduce the overall cost of the network he/she tries to procure. Within these setting we play the role of the auctioneer and our goal is to reliably procure the minimum cost network connecting our required nodes. In order to do this we need a decision algorithm, that picks out the optimal connections to buy. Since the true valuations of every connection are known only to the sellers we need our decision algorithm to be strategy proof, which makes reporting the true valuations a dominant strategy for the sellers. The problem of finding a minimum cost network connecting a set of required nodes is in essence the Steiner tree problem, which is NP-complete and has multiple greedy approximation algorithms proposed for it. We will therefore be looking at different approximation algorithms for the Steiner tree problem and check whether they are strategy proof via a Lemma proposed by Blumrosen and Nisan (Lemma 1.9 \cite{BlNi07}). In order to meet the requirements for this Lemma we need to prove Monotonicity for the respective approximation algorithm as well as finding critical payments for every edge included in the proposed solution of the algorithm.

\section{Steiner Tree Problem in Graphs}

The Steiner Problem, which was named after Jakob Steiner, has application in a lot of settings, but the most common setting is the Steiner Tree Problem in Graphs. It takes an connected, undirected, weighted Graph with non-negative edge-weights, as well as a set of vertices called "terminals" or "terminal points" and askes for the minimum weights tree connecting all terminals, called a Steiner Minimum Tree (SMT). Vertices that aren't terminals are called Steiner points and they can be included in a Steiner Tree, but their inclusion is optional as opposed to terminal points. The Steiner Tree Problem in Graphs is one of Karp's 21 NP-complete problems \cite{karp1972reducibility} and we will therefore only look at Approximation Algorithms for it. The input Graph for the Steiner Tree Problem is assumed to be complete and the cost of each edge between two vertices u and v is assumed to be the the length of the shortest path between u and v. This assumption is without loss of generality since if a connected Graph doesn't fulfill these criteria, we can just use the metric closure of it.

\section{Definitions}
The Environment for the Steiner Tree Problem in Graphs is a weighted undirected Graph G = (V, E), where V is the set of vertices in the Graph and E the set of edges. The set T $ \subseteq$ V marks the terminal vertices of G and V$\backslash$T is the set of Steiner points. The length of a given set of edges E or a given Tree X d(E)/d(X) is the sum of all edge costs. For any Set of vertices S any tree connecting S is called a Steiner Tree for S. The minimum spanning tree of S is denoted by MST(S) and its length by mst(S). Similarly a Steiner minimal tree for S is denoted by SMT(S) and its length by smt(S). A Steiner Tree is called full if all terminals are leaves in the tree and a k-restricted Steiner Tree is a full Steiner Tree that has at most k terminals. The loss of a Steiner Tree X l(X) is the length of a minimum forest spanning all vertices of X, where every component of the forest contains at least one terminal node. The contraction of a set of vertices S means to set the length of edges between vertices in S to zero. The Optimal Solution is denoted by OPT(S) and its cost by opt(S). Finally the performance ratio of an approximation algorithm is the supremum on the length of the minimum Steiner tree found by the algorithm divided by the length of an optimal solution.
\begin{equation} 
  Performance Ratio=sup(\frac{smt(T)}{opt(T)})
\end{equation}

\section{Known Algorithms and their Performance Ratios}
The first approximation for the Steiner Tree problem, which reached a performance ratio of 2 is the MST-Approximation-Algortihm by Takahashi and Hiromitsu \cite{takahashi1980approximate}. Since all other algorithms have built upon the existing Foundation and therefore every other approximation algortihm is built around this MST-Approximation. 
For a full overview of the approximation algorithm leading up to Hougardy and Proemel's approximation algorithm and their respective performance ratios see \autoref{tab:pr}
\begin{table}[htbp]
  \caption[Known Perfomance Ratios]{Known Approximation Algorithms and their Performance Ratios \cite{HoPr99}}\label{tab:pr}
  \centering
  \begin{tabular}{l l l}
    \toprule
      Author(s) & Performance Ratio & Year \\
    \midrule
      Takahashi, Hiromitsu & 2.000 & 1980 \\
      Zelikovsky & 1.834 & 1993 \\
      Berman, Ramaiyer & 1.734 & 1994 \\
      Zelikovsky & 1.694 & 1995 \\
      Proemel, Steger & 1.667 & 1997 \\
      Karpinski, Zelikovsky & 1.644 & 1997 \\
      Hougardy, Proemel & 1.598 & 1998 \\    
\bottomrule
  \end{tabular}
\end{table}
